Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
some changes to the synthesis sec

\subsection{Solution generalisation} 
Given the large soloution space to be searched during the inductive
synthesis phase, we parametrise the target language, which induces a
lattice of progressively more expressive languages.  This enables us 
to start by attempting to synthesise a program at the lowest point on this lattice
and increase the parameters of the language until we reach a point at
which the synthesis succeeds. Whenever we manage to synthesise
a candidate solution at some lower point on the lattice, 
we apply generalisation to obtain a full solution.

@@

Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a plan't precision $<I_p,F_p>$, a $k$ and a sampling rate. 
The check that these assumptions are sound 
is performed later by the {\sc complete} and {\sc sampling} 
validation stages.

@@

A set of state-space models for different classes of 
systems were extracted from the literature and employed 
for validating our automated synthesis methodology. 
All the systems are SISO models of the following form:
%
\begin{equation}
\left\lbrace\begin{array}{c}
\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
\end{array}\right.
\end{equation}

Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
translational motion. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a 
metal ball hanged in air. 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude. 
\textit{Automotive Cruise System} plant describes the model that represents 
the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the 
longitudinal motion model of a helicopter. 
\textit{Inverted Pendulum} plant describes the model of a pendulum 
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides the model for which 
a given object is suspended via a magnetic field. 
\textit{Magnetized Pointer} plant describes a model rotated through interaction 
with magnetic fields, which is typically employed in analog gauges and indicators.

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $x_{i}^{-}=-1$ and 
$x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.

>>>>

\subsection{Solution generalisation} 
Given the large soloution space to be searched during the inductive
synthesis phase, we parametrise the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesise a candidate solution at some lower point on the lattice, we
must apply some form of solution generalisation to obtain a full
solution (i.e. a solution in the original search space).

@@

Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
(blocks 1 to 5):

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. It does this by assuming a plan't
precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.

@@

\textcolor{red}{We will have to move this text to the beginning of the paper.}

A set of state-space models for different classes of systems were extracted from the literature and employed for validating our automated synthesis methodology. All the systems are SISO models of the following form:
\begin{equation}
\left\lbrace\begin{array}{c}
\dot{\textbf{x}}(t)=\textbf{A}\textbf{x}(t)+\textbf{B}u(t)\\
y(t)=\textbf{C}\textbf{x}(t)+\textbf{D}u(t)
\end{array}\right.
\end{equation}

Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}. \textit{DC Motor Position} plant describes the rotary motion that coupled with wheels and cables provides translational motion. \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension. \textit{Ball Magnetic Levitation} plant describes the magnetic field to keep a metal ball hanged in air. \textit{Buck Converter} plant represents a power converter that steps down voltage from the supply to the load while stepping up current. \textit{Boost Converter} plant also represents a power converter, but here it steps up voltage from the supply to the load while stepping down current. \textit{Buck-boost Converter} plant is a particular type of converter that has an output voltage magnitude that is either greater than or less than the input voltage magnitude. \textit{Automotive Cruise System} plant describes a system's model that represents the speed of a motor vehicle.

These benchmarks were discretized with different sample times using the approach described in the Appendix~\ref{sec:appendix}. All experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
